Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-01-30 inst/examples/20170125-Manuscript-FK.Rmd
Linkoping analysis

>>>>

```{r linkoping, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
minyear <- 1640
maxyear <- 1828
myplace <- "Linköping"
cat <- "Kungliga"
df <- df0 %>% filter(publication_place == myplace) %>%
      	      filter(catalog == cat) %>%
              filter(publication_year >= minyear &
	             publication_year <= maxyear) #%>%

tab <- unique(df[, c("publication_year", "author", "title", "publisher")])
write.table(tab, sep = "\t", quote = F, row.names = FALSE, file = "output.tables/Linkoping.tab")

p <- plot_timeline(df, x = "publication_decade", y = "titlecount") +
     ylab("Title count (n)") + ggtitle(paste("Title count: ", cat, "/", myplace))
print(p)

dfs <- df %>% select(publication_decade, publisher) %>% unique
p <- plot_timeline(dfs, x = "publication_decade") +
     ylab("Publisher count (n)") + ggtitle(paste("Publisher count: ", cat, "/", myplace))
print(p)

```
